---
title: "Covid-19 IT Dashboard"
output: 
  flexdashboard::flex_dashboard:
    navbar:
     - { title: "Use Tabs to change pages -->", align: left }
    css: www/bootstrap-pas.css
    social: ["facebook", "twitter", "linkedin"]
    logo: www/Pas_48.jpg
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
#------------------ Packages ------------------
library(flexdashboard)
library(shiny)
library(shinyjs)
library(plotly)
library(mapview)
source("www/layoutDarkP.R")
```

```{r global, include=FALSE}
`%>%` <- magrittr::`%>%`
#
#------------------ Parameters ------------------
# Set colors
# https://www.w3.org/TR/css-color-3/#svg-color
tested_color <- "purple"
positive_color <- RColorBrewer::brewer.pal(9, "PuRd")[7]
active_color <- "#1f77b4"
recovered_color <- "forestgreen"
death_color <- "#E41317"
intensive_care_color <- "#9E0003"
h_symptoms_color <- "#E41317"
home_conf_color <- "#FDBBBC"
#
#
# function to save in Rds dataset one-by-one
##%######################################################%##
#                                                          #
####                    Italy Total                     ####
#                                                          #
##%######################################################%##
#
  new_italy_total <- function() {
    italy_total <- read.csv("https://raw.githubusercontent.com/pcm-dpc/COVID-19/master/dati-andamento-nazionale/dpc-covid19-ita-andamento-nazionale.csv",
                            stringsAsFactors = FALSE) %>%
      stats::setNames(c("date_temp", "state",
                        "hospitalized_with_symptoms",
                        "intensive_care",
                        "total_hospitalized",
                        "home_confinement",
                        "cumulative_positive_cases",
                        "change_positive_cases",
                        "new_positive_cases",
                        "recovered",
                        "death",
                        "cumulative_cases",
                        "total_tests",
                        "cases_tested",
                        "notes_it", "notes_en")) %>%
      dplyr::mutate(date = lubridate::ymd(substr(date_temp, 1, 10))) %>%
      dplyr::select(-date_temp, -state, -notes_it, -notes_en, -new_positive_cases) %>%
      dplyr::select(date, dplyr::everything()) %>%
      dplyr::arrange(date)

    italy_total <- italy_total %>% 
      dplyr::arrange(date) %>%
      dplyr::mutate(tested_daily = total_tests - dplyr::lag(total_tests, n = 1)) %>%
      dplyr::mutate(new_cases_smooth = (change_positive_cases +
                                        dplyr::lag(change_positive_cases, n = 1) +
                                        dplyr::lag(change_positive_cases, n = 2) +
                                        dplyr::lag(change_positive_cases, n = 3) +
                                        dplyr::lag(change_positive_cases, n = 4)) / 5)
    
    italy_total$tested_daily[1] <- italy_total$total_tests[1]
    
    saveRDS(file='data/italy_total.rds', italy_total)
  }

##%######################################################%##
#                                                          #
####                    Italy Region                    ####
#                                                          #
##%######################################################%##
#
  new_italy_region <- function() {
    italy_region <- read.csv("https://raw.githubusercontent.com/pcm-dpc/COVID-19/master/dati-regioni/dpc-covid19-ita-regioni.csv",
                             stringsAsFactors = FALSE) %>%
      stats::setNames(c("date_temp", "state",
                        "region_code", "region_name",
                        "lat", "long",
                        "hospitalized_with_symptoms",
                        "intensive_care",
                        "total_hospitalized",
                        "home_confinement",
                        "cumulative_positive_cases",
                        "change_positive_cases",
                        "new_positive_cases",
                        "recovered",
                        "death",
                        "cumulative_cases",
                        "total_tests",
                        "cases_tested",
                        "notes_it", "notes_en")) %>%
      dplyr::mutate(date = lubridate::ymd(substr(date_temp, 1, 10))) %>%
  dplyr::select(-date_temp, - state, -notes_it, -notes_en) %>%
  dplyr::select(date, dplyr::everything()) %>%
  dplyr::mutate(region_spatial = region_name) %>%
  dplyr::group_by(region_name) %>%
  dplyr::arrange(date) %>%
  dplyr::mutate(change_d_cumcases_ptc = ((cumulative_cases/dplyr::lag(cumulative_cases, n = 1))-1)) %>%
  dplyr::mutate(change_w_cumcases_ptc = (change_d_cumcases_ptc +
                                      dplyr::lag(change_d_cumcases_ptc, n = 1) +
                                      dplyr::lag(change_d_cumcases_ptc, n = 2) +
                                      dplyr::lag(change_d_cumcases_ptc, n = 3) +
                                      dplyr::lag(change_d_cumcases_ptc, n = 4)) / 5) %>%
  dplyr::mutate(change_d_death_ptc = ((death/dplyr::lag(death, n = 1))-1)) %>%
  dplyr::mutate(new_cases_ptc_test = new_positive_cases/(total_tests-dplyr::lag(total_tests, n = 1))) %>%
  dplyr::mutate(change_w_newcases_test_ptc = (new_cases_ptc_test +
                                           dplyr::lag(new_cases_ptc_test, n = 1) +
                                           dplyr::lag(new_cases_ptc_test, n = 2) +
                                           dplyr::lag(new_cases_ptc_test, n = 3) +
                                           dplyr::lag(new_cases_ptc_test, n = 4)) / 5) %>%
  dplyr::group_by(date) %>%
  dplyr::mutate(weight_reg = new_positive_cases/sum(new_positive_cases)) %>%
  dplyr::ungroup()
  
italy_region$region_spatial <- ifelse(italy_region$region_spatial == "Emilia Romagna",
                                      "Emilia-Romagna",
                                      italy_region$region_spatial)


italy_region$region_spatial <- ifelse(italy_region$region_spatial == "Friuli Venezia Giulia",
                                      "Friuli-Venezia Giulia",
                                      italy_region$region_spatial)


italy_region$region_spatial <- ifelse(italy_region$region_spatial == "Sicilia",
                                      "Sicily",
                                      italy_region$region_spatial)

italy_region$region_spatial <- ifelse(italy_region$region_spatial == "Puglia",
                                      "Apulia",
                                      italy_region$region_spatial)


italy_region$region_spatial <- ifelse(italy_region$region_spatial == "P.A. Bolzano" |
                                        italy_region$region_spatial == "P.A. Trento",
                                      "Trentino-Alto Adige",
                                      italy_region$region_spatial)
    
    saveRDS(file='data/italy_region.rds', italy_region)
  }

##%######################################################%##
#                                                          #
####                 International data                 ####
#                                                          #
##%######################################################%##
#
#------------trajectory plot data prep------------

 new_df_trajectory <- function() {
    conf_url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"
df_conf1 <- read.csv(file = conf_url,
                     stringsAsFactors = FALSE) %>%
  dplyr::filter(Country.Region %in% c('China', 'United Kingdom','US', 'Korea, South', 'Spain', 'Brazil')) %>%
  tidyr::pivot_longer(cols = dplyr::starts_with("X"),
                      names_to = "date_temp",
                      values_to = "cases_temp")
# Parsing the date
df_conf1$month <- sub("X", "",
                      strsplit(df_conf1$date_temp, split = "\\.") %>%
                        purrr::map_chr(~.x[1]) )
df_conf1$day <- strsplit(df_conf1$date_temp, split = "\\.") %>%
  purrr::map_chr(~.x[2])
df_conf1$date <- as.Date(paste("2020", df_conf1$month, df_conf1$day, sep = "-"))
df_conf1 <- df_conf1 %>%
  dplyr::arrange(date) %>%
  dplyr::group_by(date, Country.Region) %>%
  dplyr::summarise(cases = sum(cases_temp)) %>%
  dplyr::mutate(type = "confirmed") %>%
  as.data.frame()
    df_china <- df_conf1 %>% dplyr::filter(type == "confirmed", Country.Region =='China')  %>%
      dplyr::filter(cases > 100) %>%
      dplyr::select(china = cases)

    df_china$index <- 1:nrow(df_china)

    df_us <- df_conf1 %>% dplyr::filter(type == "confirmed", Country.Region =='US')  %>%
      dplyr::filter(cases > 100) %>%
      dplyr::select(us = cases)

    df_us$index <- 1:nrow(df_us)

    df_uk <- df_conf1 %>% dplyr::filter(type == "confirmed", Country.Region =='United Kingdom')  %>%
      dplyr::filter(cases > 100) %>%
      dplyr::select(uk = cases)

    df_uk$index <- 1:nrow(df_uk)

    df_sk <- df_conf1 %>% dplyr::filter(type == "confirmed", Country.Region =='Korea, South')  %>%
      dplyr::filter(cases > 100) %>%
      dplyr::select(sk = cases)

    df_sk$index <- 1:nrow(df_sk)

    df_spain <- df_conf1 %>% dplyr::filter(type == "confirmed", Country.Region =='Spain')  %>%
      dplyr::filter(cases > 100) %>%
      dplyr::select(spain = cases)

    df_spain$index <- 1:nrow(df_spain)

    df_brazil <- df_conf1 %>% dplyr::filter(type == "confirmed", Country.Region =='Brazil')  %>%
      dplyr::filter(cases > 100) %>%
      dplyr::select(brazil = cases)

    df_brazil$index <- 1:nrow(df_brazil)

    # Read the Italy data from dataset
    df_italy <- readRDS('data/italy_total.rds') %>% dplyr::select(date, italy = cumulative_cases) %>%
      dplyr::filter(italy > 100) %>%
      dplyr::select(-date)
    df_italy$index <- 1:nrow(df_italy)

    df_trajectory <- df_china %>%
      dplyr::left_join(df_italy, by = "index") %>%
      dplyr::left_join(df_uk, by = "index") %>%
      dplyr::left_join(df_sk, by = "index") %>%
      dplyr::left_join(df_us, by = "index") %>%
      dplyr::left_join(df_brazil, by = "index") %>%
      dplyr::left_join(df_spain, by = "index")

    saveRDS(file='data/df_trajectory.rds', df_trajectory)
  }

##%######################################################%##
#                                                          #
####                  Italy Map Region                  ####
#                                                          #
##%######################################################%##

new_italy_map_region <- function() {
italy_region <- readRDS("data/italy_region.rds")
  italy_map_region <- rnaturalearth::ne_states(country = "Italy", returnclass = "sf") %>%
     dplyr::select(province = name, Region = region, geometry) %>%
     dplyr::group_by(Region) %>%
     dplyr::summarise(n = dplyr::n()) %>%
     dplyr::left_join(italy_region %>%
                        dplyr::filter(date == max(date)) %>%
                        dplyr::group_by(region_spatial) %>%
                        dplyr::select(region_spatial, "Cumulative Cases" = cumulative_cases, change_d_cumcases_ptc, "Total Deaths" = death, change_w_cumcases_ptc, weight_reg, change_d_death_ptc, new_cases_ptc_test, change_w_newcases_test_ptc) %>%
                        dplyr::mutate("Daily Change" = paste(formatC(round((100*change_d_cumcases_ptc),2), flag = "+"), "%")) %>%
                        dplyr::mutate("Last 5days average Change" = paste(formatC(round((100*change_w_cumcases_ptc),2), flag = "+"), "%")) %>%
                        dplyr::mutate("Region weight on total" = paste(formatC(round((100*weight_reg),2), flag = "+"), "%")) %>%
                        dplyr::mutate("Daily death Change" = paste(formatC(round((100*change_d_death_ptc),2), flag = "+"), "%")) %>%
                        dplyr::mutate("New cases on Tests" = paste(formatC(round((100*new_cases_ptc_test),2), flag = "+"), "%")) %>%
                        dplyr::mutate("Average Last 5days" = paste(formatC(round((100*change_w_newcases_test_ptc),2), flag = "+"), "%")) %>%
                        dplyr::select(-change_d_cumcases_ptc, -change_w_cumcases_ptc, -weight_reg, -change_d_death_ptc, new_cases_ptc_test, change_w_newcases_test_ptc) , by = c("Region" = "region_spatial"))

}

#
##%######################################################%##
#                                                          #
####               Calling the functions                ####
#                                                          #
##%######################################################%##
#
    new_italy_total()
    new_italy_region()
    new_df_trajectory()
    new_italy_map_region()

```

Summary {data-icon="ion-ios-home"}
=======================================================================
Column { data-width=150 }
-----------------------------------------------------------------------
### tested {.value-box}
```{r}
valueBoxOutput("vbox5")
```

### Positive Cases {.value-box}

```{r}
valueBoxOutput("vbox1")
```

### Active {.value-box}
```{r}
valueBoxOutput("vbox2")
```

### recovered {.value-box}
```{r}
valueBoxOutput("vbox3")
```

### Intensive Care {.value-box}
```{r}
valueBoxOutput("vbox6")
```

### death {.value-box}
```{r}
valueBoxOutput("vbox4")
```

Column { data-width=425 }
-----------------------------------------------------------------------

### Distribution of Active Cases (as of `r max(readRDS('data/italy_total.rds')$date)`)
```{r}
plotlyOutput("activecases")
```

### Daily Delta New Active Cases (variation from the day before)
```{r}
plotlyOutput("dailynew")
```

Column { data-width=425 }
-----------------------------------------------------------------------

### Overall Distribution of Cases (as of `r max(readRDS('data/italy_total.rds')$date)`)
```{r}
plotlyOutput("overall")
```


### Trajectory Plot - Italy vs. major countries (with respect of confirmed cases)
```{r}
plotlyOutput("international")
```


Regional Level {data-icon="fa-signal"}
=======================================================================

Column { data-width=500 }
-----------------------------------------------------------------------

### Cases Distribution by Region (as of `r max(readRDS('data/italy_region.rds')$date)`)
```{r}
plotlyOutput("region")
```

Column { data-width=500 }
-----------------------------------------------------------------------

### Map of Cases Distribution in Italy (as of `r max(readRDS('data/italy_region.rds')$date)`)
```{r}

mapviewOutput("italymapreg")

```

### FOCUS Lombardia: Cases Distribution (as of `r max(readRDS('data/italy_region.rds')$date)`)

```{r}
plotlyOutput("lombardia")

# ```{r echo=FALSE, results='asis'}

#cat('<div class="flourish-embed flourish-chart" data-src="story/230085"><script src="https://public.flourish.studio/resources/embed.js"></script></div>')

# dummy <- leaflet::leaflet(options = leaflet::leafletOptions(minZoom = 0, maxZoom = 18))
# 
# italy_map_region %>% 
#    mapview::mapview(zcol = "cumulative_cases")  # %>% 
#   leaflet::setView(lng =  12.49, lat = 41.9, zoom = 14)
```

About {data-icon="ion-information"}
=======================================================================

**The Coronavirus Dashboard**

This Covid19 Italy dashboard provides an overview of the 2019 Novel Coronavirus COVID-19 (2019-nCoV) outbreak in Italy.

This is a first beta release built with R.

The aim of this dashboard is to provide an insight for the business decision-makers, for that the next improvements will consider the economic impacts and the scenario analysis with a risk management point of view.

**To be updated please follow me on:**

* Twitter: <a href="https://twitter.com/pasqualemerella" target="_blank">@pasqualemerella</a>
* LinkedIn: <a href="https://www.linkedin.com/in/pasqualemerella/" target="_blank">Pasquale Merella, FRM</a>
* Instagram: <a href="https://www.instagram.com/ipas/" target="_blank">iPas</a>


**Data source**

The code of this dashboard is forked by GitHub <a href="https://github.com/RamiKrispin/" target="_blank">repository</a>.

The raw data for this dashboard is pulled from Italy Department of Civil Protection, and the coronavirus package from Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE).
The data and dashboard are refreshed on a daily basis.

For any question or feedback, please contact me via email (pasquale@merella.it) or via social.




**Pasquale Merella, FRM**

Chief Risk Officer - Green Arrow Capital SGR

Senior Fellow <a href="https://www.smartinstitute.org/" target="_blank">The Smart Institute</a> think tank

```{r, contex="server"}
# Server function
# Reading the new data and rebuild the dataset
 italy_total_new <- reactiveFileReader(180000,
                               session=session,
                               'data/italy_total.rds',
                               readRDS)

 italy_region_new <- reactiveFileReader(180000,
                               session=session,
                               'data/italy_region.rds',
                               readRDS)

 df_trajectory_new <- reactiveFileReader(180000,
                               session=session,
                               'data/df_trajectory.rds',
                               readRDS)
# Trigger functions
   observe({
        new_italy_total()
        invalidateLater(180000)
      })
   
   observe({
        new_italy_region()
        invalidateLater(180000)
      })
   
   observe({
        new_df_trajectory()
        invalidateLater(180000)
      })

# Outputs for the dashboard
output$vbox1 <- renderValueBox({
  render_value <- italy_total_new() %>% dplyr::filter(date == max(date))
  render_valuep <- italy_total_new() %>% dplyr::filter(date == max(date)-1)
  valueBox(value =  paste(format(render_value$cumulative_cases, big.mark = ","), sep = ""),
           caption = paste(" (",formatC(round(100*(render_value$cumulative_cases/render_valuep$cumulative_cases-1),1), flag = "+"), "%) Tot Positive Cases"),
           icon = "far fa-plus-square", 
           color = positive_color)
}) 

output$vbox2 <- renderValueBox({
  render_value <- italy_total_new() %>% dplyr::filter(date == max(date))
  render_valuep <- italy_total_new() %>% dplyr::filter(date == max(date)-1)
  valueBox(value = paste(format(render_value$cumulative_positive_cases, big.mark = ","), sep = ""),
           caption = paste(" (",formatC(round(100*(render_value$cumulative_positive_cases/render_valuep$cumulative_positive_cases-1),1), flag = "+"), "%) Active Cases"),
           icon = "fas fa-ambulance",
           color = active_color)
})

output$vbox3 <- renderValueBox({
  render_value <- italy_total_new() %>% dplyr::filter(date == max(date))
  render_valuep <- italy_total_new() %>% dplyr::filter(date == max(date)-1)
  valueBox(value = paste(format(render_value$recovered, big.mark = ","), sep = ""),
           caption = paste(" (",formatC(round(100*(render_value$recovered/render_valuep$recovered-1),1), flag = "+"), "%) Recovered Cases"),
           icon = "fas fa-heartbeat",
           color = recovered_color)
})

output$vbox4 <- renderValueBox({
  render_value <- italy_total_new() %>% dplyr::filter(date == max(date))
  render_valuep <- italy_total_new() %>% dplyr::filter(date == max(date)-1)
  valueBox(value = paste(format(render_value$death, big.mark = ","), sep = ""),
           caption = paste(" (",formatC(round(100*(render_value$death/render_valuep$death-1),1), flag = "+"), "%) Death Cases"),
           icon = "",
           color = death_color)
})

output$vbox5 <- renderValueBox({
  render_value <- italy_total_new() %>% dplyr::filter(date == max(date))
  render_valuep <- italy_total_new() %>% dplyr::filter(date == max(date)-1)
  valueBox(value = paste(format(render_value$total_tests, big.mark = ","), sep = ""),
         caption = paste(" (",formatC(round(100*(render_value$total_tests/render_valuep$total_tests-1),1), flag = "+"), "%) Total Tested Cases"),
         icon = "fas fa-user-md",
         color = tested_color)
})

output$vbox6 <- renderValueBox({
  render_value <- italy_total_new() %>% dplyr::filter(date == max(date))
  render_valuep <- italy_total_new() %>% dplyr::filter(date == max(date)-1)
  valueBox(value = paste(format(render_value$intensive_care, big.mark = ","), sep = ""),
         caption = paste(" (",formatC(round(100*(render_value$intensive_care/render_valuep$intensive_care-1),1), flag = "+"), "%) Intensive Care"),
         icon = "fas fa-procedures", 
         color = intensive_care_color)
})

output$activecases <- renderPlotly({
plotly::plot_ly(data = italy_total_new(),
        x = italy_total_new()$date,
        y = italy_total_new()$home_confinement, 
        name = 'Home Confinement', 
        fillcolor = '#FDBBBC',
        type = 'scatter',
        mode = 'none', 
        stackgroup = 'one') %>%
  plotly::add_trace( y = italy_total_new()$hospitalized_with_symptoms, 
             name = "Hospitalized with Symptoms",
             fillcolor = '#E41317') %>%
  plotly::add_trace(y = italy_total_new()$intensive_care, 
                name = 'Intensive Care', 
                fillcolor = '#9E0003') %>%
  plotly::layout(title = "",
         legend = list(x = 0.1, y = 0.9),
         yaxis = list(title = "Number of Cases"),
         xaxis = list(title = "Source: Italy Department of Civil Protection"),
         template = layout$template,
         hovermode = "compared")
})

output$region <- renderPlotly({
italy_region_new() %>%
  dplyr::filter(date == max(date)) %>%
  dplyr::select(region_name, cumulative_positive_cases, recovered, death, cumulative_cases) %>%
  dplyr::arrange(cumulative_cases) %>%
  dplyr::mutate(region = factor(region_name, levels = region_name)) %>%
  plotly::plot_ly(y = ~ region,
          x = ~ cumulative_positive_cases,
          orientation = 'h',
          text =  ~ cumulative_positive_cases,
          hovertemplate = paste('%{x:.0f}'),
          textposition = 'auto',
          type = "bar",
          name = "Active",
          marker = list(color = "#1f77b4")) %>%
  plotly::add_trace(x = ~ recovered,
            text =  ~ recovered,
            hovertemplate = paste('%{x:.0f}'),
            hovertemplate = paste('%{x:.0f}'),
            textposition = 'auto',
            name = "Recovered",
            marker = list(color = "forestgreen")) %>%
  plotly::add_trace(x = ~ death,
            text =  ~ death,
            hovertemplate = paste('%{x:.0f}'),
            textposition = 'auto',
            name = "Death",
            marker = list(color = "red")) %>%
  plotly::layout(title = "",
         barmode = 'stack',
         yaxis = list(title = "Region"),
         xaxis = list(title = "Number of Cases"),
         hovermode = "compare",
         template = layout$template,
         legend = list(x = 0.65, y = 0.9),
         margin =  list(
           l = 20,
           r = 10,
           b = 10,
           t = 30,
           pad = 2
         ))
})

output$dailynew <- renderPlotly({
plotly::plot_ly(data = italy_total_new(),
                x = ~ date,
                y = ~ change_positive_cases,
                type = "scatter",
                mode = "markers",
                name = "Delta Cases") %>%
  plotly::add_lines(x = ~ date,
                    y = ~ new_cases_smooth,
                    line = list(color = "red", width = 3),
                    name = "Trend Line") %>%
  plotly::layout(title = "",
                 legend = list(x = 0.01, y = 0.9),
                 yaxis = list(title = "Daily variation in number of Cases"),
                 xaxis = list(title = "Using 5 days trailing moving average to calculate the trend line"),
                 template = layout$template,
                 hovermode = "compare")
})

output$overall <- renderPlotly({
plotly::plot_ly(data = italy_total_new(),
        x = ~ date,
        y = ~cumulative_positive_cases,
        name = 'Active',
        fillcolor = '#1f77b4',
        type = 'scatter',
        mode = 'none',
        stackgroup = 'one') %>%
  plotly::add_trace( y = ~ death,
             name = "Death",
             fillcolor = '#E41317') %>%
  plotly::add_trace(y = ~recovered,
            name = 'Recovered',
            fillcolor = 'forestgreen') %>%
  plotly::layout(title = "",
         legend = list(x = 0.1, y = 0.9),
         yaxis = list(title = "Number of Cases"),
         xaxis = list(title = "Source: Italy Department of Civil Protection"),
         template = layout$template,
         hovermode = "compared")
})

output$international <- renderPlotly({
plotly::plot_ly(data = df_trajectory_new()) %>%
  plotly::add_lines(x = ~ index,
                    y = ~ china,
                    name = "China",  line = list(width = 2)) %>%
  plotly::add_lines(x = ~ index,
                    y = ~ italy,
                    line = list(color = "red", width = 4),
                    name = "Italy") %>%
  plotly::add_lines(x = ~ index,
                    y = ~ us,
                    name = "United States",  line = list(width = 2)) %>%
  plotly::add_lines(x = ~ index,
                    y = ~ uk,
                    name = "UK",  line = list(color = "orange", width = 2)) %>%
  plotly::add_lines(x = ~ index,
                    y = ~ brazil,
                    name = "Brazil",  line = list(width = 2)) %>%
  plotly::add_lines(x = ~ index,
                    y = ~ spain,
                    name = "Spain") %>%
  plotly::layout(yaxis = list(title = "Cumulative Positive Cases",type = "log"),
                 xaxis = list(title = "Days since the total positive cases surpass 100"),
                 template = layout$template,
                 legend = list(x = 0.7, y = 0.01))
})

output$lombardia <- renderPlotly({
italy_region_new() %>%
  dplyr::filter(region_name == "Lombardia") %>%
plotly::plot_ly(x = ~ date,
                y = ~cumulative_cases,
                name = 'Total',
                fill = "tozeroy",
                type = 'scattergl',
                mode = 'lines',
                stackgroup = 1) %>%
  plotly::add_trace( y = ~ cumulative_positive_cases,
                     name = "Active",
                     fill = "tozeroy",
                     type = 'scattergl',
                     mode = 'lines',
                     stackgroup = 1) %>%
  plotly::add_trace(y = ~recovered,
                    name = 'Recovered',
                    fill = "tozeroy",
                    type = 'scattergl',
                    mode = 'lines',
                    stackgroup = 1) %>%
    plotly::add_trace( y = ~ death,
                     name = "Death",
                     fill = "tozeroy",
                     type = 'scattergl',
                     mode = 'lines',
                     stackgroup = 1) %>%
  plotly::layout(title = "",
                 legend = list(x = 0.1, y = 0.9),
                 yaxis = list(title = "Number of Cases in Lombardia"),
                 xaxis = list(title = "Source: Italy Department of Civil Protection"),
                 template = layout2$template,
                 hovermode = "compared")

})

# Italy Map 
output$italymapreg <- renderMapview({
   new_italy_map_region() %>%
     mapview::mapview(zcol = "Cumulative Cases",
                      popup = leafpop::popupTable(new_italy_map_region(),
                                                  zcol = c("Region", "Cumulative Cases", "Daily Change", "Last 5days average Change", "Region weight on total", "Total Deaths", "Daily death Change", "New cases on Tests", "Average Last 5days"),
                                                  row.numbers = FALSE, feature.id = FALSE))

})

# Set this to "force" instead of TRUE for testing locally (without Shiny Server)
#    session$allowReconnect(TRUE) 
```
