---
title: "Covid-19 ITA Dashboard"
output:
  flexdashboard::flex_dashboard:
    navbar:
     - { title: "MENU -->", align: left }
    css: www/bootstrap-pas.css
    social: ["facebook", "twitter", "linkedin"]
    logo: www/Pas_48.jpg
    orientation: columns
    vertical_layout: fill
    self_contained: true
---

```{r setup, include=FALSE}
library(flexdashboard)
library(metathis)
library(leaflet)
library(leafpop)
library(Cairo)
source("www/layoutDarkP.R")
`%>%` <- magrittr::`%>%`

# Colori
tested_color      <- "purple"
positive_color    <- RColorBrewer::brewer.pal(9, "PuRd")[7]
active_color      <- "#1f77b4"
recovered_color   <- "forestgreen"
death_color       <- "#E41317"
intensive_care_color <- "#9E0003"
home_conf_color   <- "#FDBBBC"
```

```{r meta, echo=FALSE}
meta() %>%
  meta_description("Dashboard con grafici e statistiche su andamento della pandemia da Covid-19 con focus Italia e per Regione") %>%
  meta_name("github-repo" = "pasmer/italy_dash",
            "keywords"    = "dashboard, italy, Covid-19, Covid19, Italia, risk management",
            "robots"      = "index, follow",
            "author"      = "Pasquale Merella") %>%
  meta_viewport() %>%
  meta_social(
    title           = "Dashboard Covid-19 Italy",
    url             = "https://dashboard.merella.it",
    image           = "https://github.com/pasmer/italy_dash/raw/master/figures/dash1.png",
    image_alt       = "Dashboard con grafici e statistiche",
    og_type         = "Dashboard",
    og_author       = "Pasquale Merella",
    twitter_card_type = "summary",
    twitter_creator = "@pasqualemerella"
  ) %>%
  include_meta()
```

```{r load_data, include=FALSE}
# Legge i dati dai file RDS pre-salvati (dati storici COVID-19)
italy_total      <- readRDS("data/italy_total.rds")
italy_region     <- readRDS("data/italy_region.rds")
df_traj_abs      <- readRDS("data/df_trajectory.rds")
italy_map_region <- readRDS("data/italy_map_region.rds")

# Data di riferimento
datanew <- as.character(max(italy_total$date))

# Ultimi due giorni per i value box
vb_today <- italy_total %>% dplyr::filter(date == max(date))
vb_prev  <- italy_total %>% dplyr::filter(date == max(date) - 1)

# Lombardia
lomb_today <- italy_region %>% dplyr::filter(date == max(date) & region_spatial == "Lombardia")
```

HOME {data-icon="ion-ios-home"}
=======================================================================

Column { data-width=150 }
-----------------------------------------------------------------------

### tested {.value-box}
```{r}
valueBox(
  value   = format(vb_today$total_tests, big.mark = ","),
  caption = paste0(" (", formatC(round(100*(vb_today$total_tests/vb_prev$total_tests-1),1), flag="+"), "%) Total Tested Cases"),
  icon    = "fas fa-user-md",
  color   = tested_color
)
```

### Positive Cases {.value-box}
```{r}
valueBox(
  value   = format(vb_today$cumulative_cases, big.mark = ","),
  caption = paste0(" (", formatC(round(100*(vb_today$cumulative_cases/vb_prev$cumulative_cases-1),1), flag="+"), "%) Tot Positive Cases"),
  icon    = "far fa-plus-square",
  color   = positive_color
)
```

### new cases {.value-box}
```{r}
valueBox(
  value   = format(vb_today$new_positive_cases, big.mark = ","),
  caption = paste0("New Cases of which ", lomb_today$new_positive_cases, " in Lombardy"),
  icon    = "fas fa-search",
  color   = intensive_care_color
)
```

### Active {.value-box}
```{r}
valueBox(
  value   = format(vb_today$cumulative_positive_cases, big.mark = ","),
  caption = paste0(" (", formatC(round(100*(vb_today$cumulative_positive_cases/vb_prev$cumulative_positive_cases-1),1), flag="+"), "%) Active Cases"),
  icon    = "fas fa-ambulance",
  color   = active_color
)
```

### recovered {.value-box}
```{r}
valueBox(
  value   = format(vb_today$recovered, big.mark = ","),
  caption = paste0(" (", formatC(round(100*(vb_today$recovered/vb_prev$recovered-1),1), flag="+"), "%) Recovered Cases"),
  icon    = "fas fa-heartbeat",
  color   = recovered_color
)
```

### Intensive Care {.value-box}
```{r}
valueBox(
  value   = format(vb_today$intensive_care, big.mark = ","),
  caption = paste0(" (", formatC(round(100*(vb_today$intensive_care/vb_prev$intensive_care-1),1), flag="+"), "%) Intensive Care"),
  icon    = "fas fa-procedures",
  color   = intensive_care_color
)
```

### death {.value-box}
```{r}
valueBox(
  value   = format(vb_today$death, big.mark = ","),
  caption = paste0(" (", formatC(round(100*(vb_today$death/vb_prev$death-1),1), flag="+"), "%) Death Cases"),
  icon    = "",
  color   = death_color
)
```

Column { data-width=425 }
-----------------------------------------------------------------------

### `r paste("Absorption Rate of Cases - Italy vs. major countries (as of", datanew, ")")`
```{r}
plotly::plot_ly(data = df_traj_abs) %>%
  plotly::add_lines(x = ~index, y = ~round(100*abs_italy,1),   line = list(color="red", width=4), name="Italy") %>%
  plotly::add_lines(x = ~index, y = ~round(100*abs_germany,1), line = list(width=2), name="Germany") %>%
  plotly::add_lines(x = ~index, y = ~round(100*abs_us,1),      name="USA",    line = list(width=2)) %>%
  plotly::add_lines(x = ~index, y = ~round(100*abs_bra,1),     name="Brazil", line = list(color='blue', width=2)) %>%
  plotly::add_lines(x = ~index, y = ~round(100*abs_china,1),   name="China",  line = list(width=2)) %>%
  plotly::add_lines(x = ~index, y = ~round(100*abs_russia,1),  name="Russia", line = list(width=2)) %>%
  plotly::add_lines(x = ~index, y = ~round(100*abs_japan,1),   name="Japan",  line = list(width=2)) %>%
  plotly::add_lines(x = ~index, y = ~round(100*abs_france,1),  name="France", line = list(width=2)) %>%
  plotly::add_lines(x = ~index, y = ~round(100*abs_spain,1),   name="Spain",  line = list(width=2)) %>%
  plotly::add_lines(x = ~index, y = ~round(100*abs_belgium,1), name="Belgium",line = list(width=2)) %>%
  plotly::layout(
    yaxis = list(title="Absorption Rate of Cases", ticksuffix="%"),
    xaxis = list(title="Days since total positive cases surpassed 100"),
    template = layout$template, hovermode="compared",
    legend = list(x=0.01, y=1.2))
```

### ITALY Daily Delta New Active Cases (variation from the day before)
```{r}
plotly::plot_ly(data = italy_total, x = ~date, y = ~change_positive_cases,
                type="scatter", mode="markers", name="Delta Cases") %>%
  plotly::add_lines(x = ~date, y = ~new_cases_smooth,
                    line = list(color="red", width=3), name="Trend Line") %>%
  plotly::layout(
    yaxis = list(title="Daily variation in number of Cases"),
    xaxis = list(title="Using 5 days trailing moving average to calculate the trend line"),
    template = layout$template, hovermode="compare",
    legend = list(x=0.01, y=0.9))
```

Column { data-width=425 }
-----------------------------------------------------------------------

### `r paste("Conditional Mortality Rate - Italy vs. major countries (as of", datanew, ")")`
```{r}
plotly::plot_ly(data = df_traj_abs) %>%
  plotly::add_lines(x = ~index, y = ~round(100*death_italy,1),   line = list(color="red", width=4), name="Italy") %>%
  plotly::add_lines(x = ~index, y = ~round(100*death_germany,1), line = list(width=2), name="Germany") %>%
  plotly::add_lines(x = ~index, y = ~round(100*death_us,1),      name="USA",    line = list(width=2)) %>%
  plotly::add_lines(x = ~index, y = ~round(100*death_bra,1),     name="Brazil", line = list(color='blue', width=2)) %>%
  plotly::add_lines(x = ~index, y = ~round(100*death_china,1),   name="China",  line = list(width=2)) %>%
  plotly::add_lines(x = ~index, y = ~round(100*death_russia,1),  name="Russia", line = list(width=2)) %>%
  plotly::add_lines(x = ~index, y = ~round(100*death_japan,1),   name="Japan",  line = list(width=2)) %>%
  plotly::add_lines(x = ~index, y = ~round(100*death_france,1),  name="France", line = list(width=2)) %>%
  plotly::add_lines(x = ~index, y = ~round(100*death_spain,1),   name="Spain",  line = list(width=2)) %>%
  plotly::add_lines(x = ~index, y = ~round(100*death_belgium,1), name="Belgium",line = list(width=2)) %>%
  plotly::layout(
    yaxis = list(title="Conditional Mortality Rate", ticksuffix="%"),
    xaxis = list(title="Days since total positive cases surpassed 100"),
    template = layout$template, hovermode="compared",
    legend = list(x=0.7, y=1.2))
```

### `r paste("ITALY Overall Distribution of Cases (as of", datanew, ")")`
```{r}
plotly::plot_ly(data = italy_total, x = ~date) %>%
  plotly::add_trace(y = ~cumulative_positive_cases, name='Active',    fillcolor='#1f77b4',   type='scatter', mode='none', stackgroup='one') %>%
  plotly::add_trace(y = ~death,                     name="Death",     fillcolor='#E41317',   type='scatter', mode='none', stackgroup='one') %>%
  plotly::add_trace(y = ~recovered,                 name='Recovered', fillcolor='forestgreen',type='scatter',mode='none', stackgroup='one') %>%
  plotly::layout(
    yaxis = list(title="Number of Cases"),
    xaxis = list(title="Source: Italy Department of Civil Protection"),
    template = layout$template, hovermode="compared",
    legend = list(x=0.1, y=0.9))
```

Regional DATA {data-icon="fa-signal"}
=======================================================================

Column { data-width=500 }
-----------------------------------------------------------------------

### `r paste("Top10 Cases Distribution by Region (as of", datanew, ")")`
```{r}
italy_region %>%
  dplyr::filter(date == max(date)) %>%
  dplyr::select(region_spatial, cumulative_positive_cases, recovered, death, cumulative_cases) %>%
  dplyr::group_by(region_spatial) %>%
  dplyr::summarise(cumulative_positive_cases = sum(cumulative_positive_cases),
                   recovered = sum(recovered), death = sum(death),
                   cumulative_cases = sum(cumulative_cases)) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(cumulative_cases) %>%
  dplyr::top_n(10) %>%
  dplyr::mutate(region = factor(region_spatial, levels = region_spatial)) %>%
  plotly::plot_ly(y = ~region, x = ~cumulative_positive_cases, orientation='h',
          text = ~cumulative_positive_cases, hovertemplate='%{x:.0f}',
          textposition='auto', type="bar", name="Active",
          marker = list(color="#1f77b4")) %>%
  plotly::add_trace(x = ~recovered, text = ~recovered, hovertemplate='%{x:.0f}',
            textposition='auto', name="Recovered", marker=list(color="forestgreen")) %>%
  plotly::add_trace(x = ~death, text = ~death, hovertemplate='%{x:.0f}',
            textposition='auto', name="Death", marker=list(color="red")) %>%
  plotly::layout(barmode='stack', yaxis=list(title="Region"),
         xaxis=list(title="Number of Cases"), hovermode="compare",
         template=layout$template, legend=list(x=0.65, y=0.9),
         margin=list(l=20,r=10,b=10,t=30,pad=2))
```

### `r paste("Top10 Cases Distribution based on population (as of", datanew, ")")`
```{r}
italy_region_pop <- data.frame(
  region_spatial = c("Lombardia","Lazio","Campania","Sicily","Veneto",
                     "Emilia-Romagna","Piemonte","Apulia","Toscana",
                     "Calabria","Sardegna","Liguria","Marche","Abruzzo",
                     "Friuli-Venezia Giulia","Trentino-Alto Adige",
                     "Umbria","Basilicata","Molise","Valle d'Aosta"),
  pop = c(10006099,5720214,5624528,4804719,4870059,4464119,4240773,
          3924283,3677048,1843712,1590897,1503418,1488416,1276572,
          1196769,1084006,852263,534960,287678,123425),
  stringsAsFactors = FALSE
)
italy_region %>%
  dplyr::filter(date == max(date)) %>%
  dplyr::select(date, region_spatial, death, cumulative_cases) %>%
  dplyr::group_by(region_spatial) %>%
  dplyr::summarise(death=sum(death), cumulative_cases=sum(cumulative_cases)) %>%
  dplyr::left_join(italy_region_pop, by="region_spatial") %>%
  dplyr::mutate(Death_on_pop=(death/pop)*100000, Tot_cases_on_pop=(cumulative_cases/pop)*100000) %>%
  dplyr::arrange(Tot_cases_on_pop) %>% dplyr::top_n(10) %>%
  dplyr::mutate(region=factor(region_spatial, levels=unique(region_spatial)[order(Tot_cases_on_pop,decreasing=TRUE)])) %>%
  plotly::plot_ly(x=~region, y=~Tot_cases_on_pop, type='bar', name="Total Cases",
          marker=list(color="#1f77b4"), orientation='v') %>%
  plotly::add_trace(y=~Death_on_pop, type='bar', name="Death Cases",
            marker=list(color="red"), orientation='v') %>%
  plotly::layout(yaxis=list(title="Number of Cases per 100k residents"),
         xaxis=list(title="Source: Italy Department of Civil Protection"),
         template=layout3$template, hovermode="compared",
         legend=list(x=0.5, y=0.9))
```

Column { data-width=500 }
-----------------------------------------------------------------------

### `r paste("Map of Cases Distribution in Italy (as of", datanew, ")")`
```{r}
IT <- italy_map_region
mapview::mapview(
  IT, zcol = "Cum. Cases",
  popup = leafpop::popupTable(
    IT,
    zcol = c("Region","Cum. Cases","Daily Change","Average change Last 5days",
             "Region weight on total","Total Deaths","Daily death Change",
             "New cases on Tests","Average Last 5days"),
    row.numbers = FALSE, feature.id = FALSE
  )
)@map
```

### `r paste("FOCUS Lombardia: Cases Distribution (as of", datanew, ")")`
```{r}
italy_region %>%
  dplyr::filter(region_name == "Lombardia") %>%
  plotly::plot_ly(x = ~date) %>%
  plotly::add_trace(y=~cumulative_cases,          name='Total',     fill="tozeroy", type='scattergl', mode='lines', stackgroup=1) %>%
  plotly::add_trace(y=~cumulative_positive_cases, name="Active",    fill="tozeroy", type='scattergl', mode='lines', stackgroup=1) %>%
  plotly::add_trace(y=~recovered,                 name='Recovered', fill="tozeroy", type='scattergl', mode='lines', stackgroup=1) %>%
  plotly::add_trace(y=~death,                     name="Death",     fill="tozeroy", type='scattergl', mode='lines', stackgroup=1) %>%
  plotly::layout(
    yaxis=list(title="Number of Cases in Lombardia"),
    xaxis=list(title="Source: Italy Department of Civil Protection"),
    template=layout2$template, hovermode="compared",
    legend=list(x=0.1, y=0.9))
```

About {data-icon="ion-information"}
=======================================================================

**The Coronavirus Dashboard**

This Covid19 Italy dashboard provides an overview of the 2019 Novel Coronavirus COVID-19 (2019-nCoV) outbreak in Italy. Data is frozen at the last update of the official Italian Civil Protection dataset.

I built this dashboard with R then I deployed it as a static self-contained HTML on UmbrelOS (Raspberry Pi).

The aim of this dashboard is to provide an insight for the <b>business decision-makers</b>, with a <b>risk management</b> point of view.

**Follow me on:**

* Twitter: <a href="https://twitter.com/pasqualemerella" target="_blank">@pasqualemerella</a>
* LinkedIn: <a href="https://www.linkedin.com/in/pasqualemerella/" target="_blank">Pasquale Merella, FRM</a>
* Instagram: <a href="https://www.instagram.com/ipas/" target="_blank">iPas</a>

**Data source**

Raw data from Italy Department of Civil Protection and JHU CCSE. Full code on <a href="https://github.com/pasmer/italy_dash" target="_blank">GitHub</a>.

**Pasquale Merella, FRM** — Chief Risk Officer
